--- 
title: "R Training"
author: "Jimmy Briggs"
date: "`r Sys.Date()`"
site: https:/bookdown.org/jimbrig2011/r_training/
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "R Training Resources, Guides, Tips, and Knowledge Base."
---

# Introduction

### Contents

+ [Package HomePage](https://jimbrig.github.io/rtraining/) 
+ [R Setup Guide](https://jimbrig.github.io/rtraining/articles/setting-up-r.html) 
+ [R Shiny Training Resources](https://jimbrig.github.io/rtraining/articles/shiny-training.html) 
+ [List of Helpful Bookdowns](https://jimbrig.github.io/rtraining/articles/bookdown-list.html) 

***

<!-- description: start -->
Package {rtraining}: R Training Resources, Guides, Tips, and Knowledge Base.  
Current version is 0.0.1.  

***

The goal of `rtraining` is to provide useful resources, knowledge, and 
walkthroughs for new R developers.  

The package is split into three main areas:

1. R Setup and Configuration: a thorough walkthrough for setting up and 
configuring R, RStudio, and various other software in an efficient manner.

2. R Workflows: example workflows showcasing the main types of work done with R,
including, but not limited to R Data Analysis Projects, Reporting with RMarkdown,
R Shiny Applications, R Package Development.
  
3. R Tips & Tricks: General tips and tricks learned over time from my experiences
with R.

<!-- description: end -->

## Installation
<!-- install: start -->

You can install the released version of rtraining from 
[CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rtraining")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jimbrig/rtraining")
```

***

The list of dependencies required to install this package is: attachment, chameleon, devtools, knitr, pkgdown, rmarkdown, roxygen2, utils, xfun.

To install the package, you can run the following script

```{r, echo=TRUE, eval=FALSE}
# install.packages("remotes")
remotes::install_local(path = "rtraining_0.0.1.tar.gz")
```

In case something went wrong, you may want to install dependencies before using:

```{r, echo=TRUE, eval=FALSE}
# Remotes ----
install.packages("remotes")
remotes::install_github('ThinkR-open/chameleon')
# Attachments ----
to_install <- c("xfun")
  for (i in to_install) {
    message(paste("looking for ", i))
    if (!requireNamespace(i)) {
      message(paste("     installing", i))
      install.packages(i)
    }
  }
```

Once you have the package installed you can open the website directly by running:

```{r run_pkgdown, eval=FALSE}
library(rtraining)
rtraining::open_pkgdown()
```


Similarly you can open the package `bookdown` with:

```{r run_guide, eval=FALSE}
rtraining::open_guide()
```

<!-- install: end -->


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
